Verification in Isabelle/HOL of a Set-based Algorithm for Computing Strongly Connected Components

### 2022-09-21 cpp/submission.tex
Added some lines in the conclusion

We summarize the overall effort of the proof in number of lines of the Isabelle theory (definitions / proofs) in a table for each main category.

@@

\begin{itemize}
\item successfully proved correctness of an efficient sequential SCC algorithm
\item compare to Tarjan proof (Chen et al.): both are DFS algorithms, the algorithm considered here collapses loops as soon as they are found, minimizing stack size
\item compare to Lammich's work: he exploits the refinement framework for deriving executable code, we work on a higher-level representation of the algorithm as elementary recursive functions, hence invariants are simpler
\item objective: stepping stone towards a proof of the parallel version of the algorithm from Bloemen's thesis -- understand which invariants can be relaxed.
\end{itemize}

>>>>

We summarize the overall effort of the proof in number of lines (definitions / proofs) for each main category.

@@

As a result of this whole year of work, we successfully proved correctness of an efficient sequential set-based SCC algorithm. In comparison to Tarjan's algorithm whose formal proof was written by Chen et. al \cite{chen:tarjan}, this algorithm collapses loops as soon as they are found, thus minimizing the stack size. Our formalization and  proof in Isabelle are quite similar to theirs as they are based on higher-level representations of the algorithms as elementary recursive functions. Hence, our invariants are quite simple compared to those expressed in Lammich's work \cite{lammich:gabow} since he exploits the refinement framework for deriving executable code, resulting in implementable-like representations that make expressing invariants more difficult from a higher-level point of view.

% \begin{itemize}
% \item successfully proved correctness of an efficient sequential SCC algorithm
% \item compare to Tarjan proof (Chen et al.): both are DFS algorithms, the algorithm considered here collapses loops as soon as they are found, minimizing stack size
% \item compare to Lammich's work: he exploits the refinement framework for deriving executable code, we work on a higher-level representation of the algorithm as elementary recursive functions, hence invariants are simpler
% \item objective: stepping stone towards a proof of the parallel version of the algorithm from Bloemen's thesis -- understand which invariants can be relaxed.
% \end{itemize}
